Appendix to 'Detecting social information in a dense database of infants’ natural

### 2022-01-06 paper/preprint/appendix.Rmd
fix roc curves figure

```{r}
ggarrange(face_roc, hand_roc, nrow=1)
```

@@

# density plot of OP's false positive face/hand locations
p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # could actually overplot all the face rectangles? prob very messy...
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Mean x-position of OpenPose Detection") + 
  ylab("Mean y-position of OpenPose Detection") + 
  ggtitle("Face False Positives") + theme(legend.position = "none")

p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # top-left is 0,0
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Mean x-position of OpenPose Detection") + 
  ylab("Mean y-position of OpenPose Detection") + 
  ggtitle("Hand False Positives") + theme(legend.position = "none")

>>>>

```{r roc_curves, fig.width=6.5, fig.height=3.2, fig.cap="ROC curves relating the rate of true vs. false positives for both face and hand detections at each level of detector confidence thresholds (lighter values = stricter cutoffs)."}
ggarrange(face_roc, hand_roc, nrow=1)
```

@@

# density plot of OP's false positive face/hand locations
p1 <- ddd %>% filter(face_eval_ketan=="FP", label=="face") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # could actually overplot all the face rectangles? prob very messy...
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Mean x-position of OpenPose Detection") + 
  ylab("Mean y-position of OpenPose Detection") + 
  ggtitle("Face False Positives") + theme(legend.position = "none") +
  +
  scale_y_reverse()

p2 <- ddd %>% filter(hand_eval_ketan=="FP", label=="hand") %>%
  mutate(x=left+0.5*width,
         y=1-(top+0.5*height)) %>% # top-left is 0,0
  ggplot(aes(x=x, y=y, fill=..level..)) + 
  stat_density_2d(geom = "polygon") + xlim(-.05,1.05) + ylim(-.05,1.0) + 
  xlab("Mean x-position of OpenPose Detection") + 
  ylab("Mean y-position of OpenPose Detection") + 
  ggtitle("Hand False Positives") + theme(legend.position = "none") +
  +
  scale_y_reverse()
